Something

### 2019-05-10 cysep-eurosp/abstract.tex
adds some sections in abstract

\textbf{More detailed approach:} 
By running a distance bounding scheme with anonymous credentials,
physically present persons (such as protest participants) and create proof
shares. This is done using smartphones with (assumed)
distance-bounding chips, without Internet connection but using any
available local communications. Before and after the event (protest), participants (and
witnesses), interact with a public blockchain (which does require
Internet access, and anonymization by e.g. Tor). Before the event to get
a timestamp and after the event to upload proof shares, again with a
time stamp. The proof shares form verifiable yet privacy-preserving
participation proofs according to counting criteria. These criteria
(time interval, location range, number or kind (e.g., anyone, trusted
journalists) of unique proof shares
needed for a proof)

@@

\textbf{Relation to theme:} both security and privacy: verifiability

\textbf{Why it could spark discussions:}
practical problems: sybil-proof identities needed for anonymous
credentials

\textbf{Information about the presenters:} Daniel Bosk is a PhD
student and Sonja Buchegger a Computer Science professor, both at the
division of Theoretical Computer Science at KTH Royal Institute of
Technology.

>>>>

\textbf{More detailed approach:} 
By running a distance bounding scheme with anonymous credentials,
physically present persons (such as protest participants) and create proof
shares. This is done using smartphones with (assumed)
distance-bounding chips, without Internet connection but using any
available local communications. Before and after the event (protest), participants (and
witnesses), interact with a public ledger such as a blockchain (which does require
Internet access, and anonymization by e.g. Tor). Before the event to get
a timestamp and after the event to upload proof shares, again with a
time stamp. The proof shares form verifiable yet privacy-preserving
participation proofs according to counting eligibility criteria. These criteria, including
time interval, location range, number or kind (e.g., anyone, trusted
journalists) of unique proof shares
needed for a proof, enable verification by recount. Counting is done
by downloading the proof shares from the ledger, checking the validity
and eligibility, and summing up. Any published counts need to also
publish the criteria used to be verified, but anyone could decide on
their own criteria and count accordingly.

@@

\textbf{Relation to theme:} This work is concerned with both security
and privacy: accountability and verifiability (individual, universal, eligibility) and
privacy (unlinkability to individual, unlinkability between events,
unlinkability between witnessing instances).

\textbf{Why it could spark discussions:}
practical/ideological problems: sybil-proof identities needed for anonymous
credentials

\textbf{Information about the presenters:} Daniel Bosk is a PhD
student and Sonja Buchegger a Computer Science professor, both at the
division of Theoretical Computer Science at KTH Royal Institute of
Technology, working on privacy-enhancing technologies.
